---
title: "Trash fish quality analysis"
format: html
---

#Preperation 
##Load packages
```{r}
library(tidyverse)
library(ggplot2)
library(car)
library(glmmTMB)
library(mgcv)
library(mgcViz)
library(multcomp)
library(emmeans)
library(DHARMa)
library(powerjoin)
library(paletteer)
library(fishualize)
library(vegan)
library(ggsignif)
library(ggpubr)
library(reshape2)
library("Hmisc")
library(corrplot)

set.seed(42)
```

##Load data
```{r}
quality_chem <- read_csv('../data/1.3-2024-1-1_Chem-Bio-indicators.csv', trim_ws = TRUE, na = c("", "na"))
quality_sense <- read_csv('../data/1.3-2024-1-1_TF_sensory_scores.csv', trim_ws = TRUE, na = c("", "na"))
quality_sp <- read_csv('../data/1.3-2024-1-1_TF_indicators_species.csv', trim_ws = TRUE, na = c("", "na"))

quality_chem <- quality_chem |>  
  dplyr::mutate(location = as.factor(location), 
                replicate = as.factor(replicate), 
                sample  = as.factor(sample))

quality_sense <- quality_sense |>  
  dplyr::mutate(location = as.factor(location), 
                evaluator = as.factor(evaluator),
                sample  = as.factor(sample),
                Score = (Eye_Clarity+Mucous+Odor)/3)

quality_sp <- quality_sp |>  
  dplyr::mutate(location = as.factor(location)) |> 
  dplyr::group_by(sample) |> 
  dplyr::mutate(total_count = sum(Count), 
                proportion = Count/total_count)
``` 

###Combine datasets 
```{r}
quality_sense_mean <- 
  quality_sense |>  
  dplyr::mutate(score = (Eye_Clarity+Mucous+Odor)/3) |>  
  dplyr::group_by(sample, location) |>  
  dplyr::summarise(score = mean(score), 
                   eye = mean(Eye_Clarity), 
                   mucous = mean(Mucous), 
                   odor = mean(Odor)) 

quality_comb <- power_full_join(quality_chem, quality_sense_mean, 
                     by = "sample") |>  
  dplyr::select(!location.y) |> 
  dplyr::rename(location = location.x)

quality_comb_mean <- quality_comb |> 
  dplyr::select(!replicate) |> 
  dplyr::group_by(sample, location) |>  
  dplyr::summarise(across(everything(), mean, na.rm = TRUE)) 

quality_Family <- 
  quality_sp |>  
  dplyr::group_by(Number, sample, location, Type, Family) |> 
  dplyr::summarise(Proportion = sum(proportion))
```

#Species composition
```{r}
quality_sp |> 
  dplyr::group_by(Genus) |> 
  dplyr::summarise(sum(Count))

#52 Genera including Unknown, for 51 total (48 if you exclude the prawn, squid and stingray)

q_fam_order <- quality_Family |> 
  dplyr::group_by(Family) |> 
  dplyr::summarise(overP = sum(Proportion)/22) |> 
  arrange(desc(overP)) |> 
  dplyr::mutate(Index = 1:n(), Sum_Fam = ifelse(Index > 9, "Other", Family)) |> 
    power_full_join(quality_Family, 
                     by = "Family") |>  
  dplyr::group_by(Number,location, Sum_Fam, Index) |> 
  dplyr::summarise(Prop = sum(Proportion))
 
#Bubble plot summarising families per sample 
q_fam_order |> 
  ggplot(aes(y = fct_reorder(Sum_Fam, Index, .desc = TRUE), x = Number, size = Prop, colour = location)) + 
  geom_point() + 
  theme_pubr() +
  theme(panel.grid.major = element_line(color = "lightgrey",
                                        size = 0.2)) +
  scale_x_continuous(name = "Trash fish sample", 
                     breaks = c(seq(from =1, to = 22, by =1)), 
                     limits = c(1,22)) +
  scale_y_discrete(name = "Trash Fish Family") +
  scale_colour_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location", 
                           #guide = "none"
                           ) + 
  scale_size_continuous(name = "Proportion of sample")
```


#Sensory Assessment
###Evaluators 
####Eye Clarity
```{r}
quality_sense |>  
  ggplot(aes(sample, Eye_Clarity)) +
  geom_point(aes(colour = evaluator)) + 
  scale_y_continuous(breaks=c(seq(0,10,1)), 
                     limits = c(0,10))
  
glm_evaluators_eye <- glmmTMB(Eye_Clarity ~ evaluator, 
                              data = quality_sense,
                              family = gaussian())
#checking fit
simulateResiduals(glm_evaluators_eye, plot = TRUE)     #outlier detected,  acknowledge
hist(simulateResiduals(glm_evaluators_eye))            #good
testZeroInflation(glm_evaluators_eye)                  #good

summary(glm_evaluators_eye)
#no effect
```

####Mucous
```{r}
quality_sense |>  
  ggplot(aes(x = evaluator, y = Mucous, colour = evaluator)) +
  geom_boxplot()
  
glm_evaluators_mucous <- glmmTMB(Mucous ~ evaluator, 
                              data = quality_sense,
                              family = gaussian(), 
                              dispformula = ~evaluator)

#checking fit
simulateResiduals(glm_evaluators_mucous, plot = TRUE)     #KS triggered but line mostly OK
hist(simulateResiduals(glm_evaluators_mucous))            #good

summary(glm_evaluators_mucous)
#no effect
```

####Odor
```{r}
quality_sense |>  
  ggplot(aes(sample, Odor)) +
  geom_point(aes(colour = evaluator)) + 
  scale_y_continuous(breaks=c(seq(0,10,1)), 
                     limits = c(0,10)) + 
  facet_wrap(~ location)
  
glm_evaluators_odor <- glmmTMB(log(Odor) ~ evaluator, 
                              data = quality_sense,
                              family = gaussian(), 
                              dispformula = ~location)
#checking fit
simulateResiduals(glm_evaluators_odor, plot = TRUE)     #works with log and dis= ~location
hist(simulateResiduals(glm_evaluators_odor))            #good

summary(glm_evaluators_odor)
#no effect
```

####Overall score
```{r}
##No significant differences in evaluators scoring for all variables
#Odor has the most variation, followed by eye clarity. Mucous very consistent  
glm_evaluators_score <- glmmTMB(Score ~ evaluator, 
                              data = quality_sense,
                              family = gaussian())

simulateResiduals(glm_evaluators_score, plot = TRUE)     #good
hist(simulateResiduals(glm_evaluators_score))            #good

summary(glm_evaluators_score)
#no effect of evaluators on overall score 
```

###Scores 
####Plot together
```{r}
quality_sense_melt <- quality_sense |>  
  reshape2::melt(ids.vars=c('sample', 'location', 'evaluator'), value.vars=c('Eye_Clarity', 'Mucous', 'Odor', 'Score')) |>  
  dplyr::group_by(sample, location, variable) |> 
  dplyr::summarise(value = mean(value))

quality_sense_melt |> 
ggplot(aes(x = variable, y = value, fill = location)) + 
  geom_boxplot() +
  theme_minimal() + 
  scale_x_discrete(name = "", 
                   labels = c("Eye Clarity", "Mucous", "Odor", "Overall Score")) + 
  scale_y_continuous(limits = c(1, 10), 
                     breaks = seq(1, 10, 1), 
                     name = "Score") + 
  scale_fill_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black", 
                                   size = 12), 
        axis.text = element_text(colour = "black", 
                                 size = 12), 
        axis.title = element_text(size = 12),
        panel.grid = element_blank(), 
        axis.ticks = element_line(colour = "black"), 
        panel.grid.major = element_line(colour = "#e5e5e5"), 
        legend.position = "bottom")

```

###Location 
####Eye clarity
#####Ba Ria - Vung Tau
```{r}
quality_sense_only_BRVT <- quality_sense |> 
  dplyr::filter(location == "Ba Ria - Vung Tau" ) 

glm_eye_BRVT <- glmmTMB(Eye_Clarity ~ sample + (1|evaluator),
                              data = quality_sense_only_BRVT,
                              family = gaussian())

simulateResiduals(glm_eye_BRVT, plot = TRUE)     #triggered but visually OK
hist(simulateResiduals(glm_eye_BRVT))            #good
testDispersion(simulateResiduals(glm_eye_BRVT))            #good

summary(glm_eye_BRVT)
cld((emmeans(glm_eye_BRVT,  ~ sample)), Letters = letters)
 #Differences between farms exist
```

#####Kien Giang
```{r}
quality_sense_only_KG <- quality_sense |> 
  dplyr::filter(location == "Kien Giang" ) 

glm_eye_KG <- glmmTMB(Eye_Clarity ~ sample + (1|evaluator),
                              data = quality_sense_only_KG,
                              family = gaussian())

simulateResiduals(glm_eye_KG, plot = TRUE)     #good
hist(simulateResiduals(glm_eye_KG))            #good
testZeroInflation(glm_eye_KG)                  #good

summary(glm_eye_KG)
cld((emmeans(glm_eye_KG,  ~ sample)), Letters = letters)
#Differences between farms exist
```

#####Ca Mau
```{r}
quality_sense_only_CM <- quality_sense |> 
  dplyr::filter(location == "Ca Mau" ) 

glm_eye_CM <- glmmTMB(Eye_Clarity ~ sample + (1|evaluator),
                              data = quality_sense_only_CM,
                              family = gaussian())

simulateResiduals(glm_eye_CM, plot = TRUE)     #good
hist(simulateResiduals(glm_eye_CM))            #good
testZeroInflation(glm_eye_CM)                  #good

summary(glm_eye_CM)
cld((emmeans(glm_eye_CM,  ~ sample)), Letters = letters)
#Differences between farms exist 
```

#####Between regions
```{r}
quality_sense |> 
ggplot(aes(x = location, y = Eye_Clarity, fill = location)) + 
  geom_boxplot()

glm_eye_locations <- glmmTMB(Eye_Clarity ~ location + (1|evaluator),
                              data = quality_sense,
                              family = gaussian())

simulateResiduals(glm_eye_locations, plot = TRUE)     #good - but outlier detected
hist(simulateResiduals(glm_eye_locations))            #good
testDispersion(simulateResiduals(glm_eye_locations))            #good

summary(glm_eye_locations)
cld((emmeans(glm_eye_locations,  ~ location, type = "response")), Letters = letters)
 # location          response    SE  df lower.CL upper.CL .group
# Ba Ria - Vung Tau   5.33 0.217 Inf      4.90      5.75  a    
#  Kien Giang          5.98 0.204 Inf      5.58      6.38  ab   
#  Ca Mau              6.70 0.274 Inf      6.16      7.24   b
```

####Mucous
#####Ba Ria - Vung Tau
```{r}
quality_sense_only_BRVT <- quality_sense |> 
  dplyr::filter(location == "Ba Ria - Vung Tau" ) 

glm_mucous_BRVT <- glmmTMB(Mucous ~ sample + (1|evaluator),
                              data = quality_sense_only_BRVT,
                              family = gaussian())

simulateResiduals(glm_mucous_BRVT, plot = TRUE)     #good
hist(simulateResiduals(glm_mucous_BRVT))            #good
testDispersion(simulateResiduals(glm_mucous_BRVT))            #good

cld((emmeans(glm_mucous_BRVT,  ~ sample)), Letters = letters)
#Differences between farms exist
```

#####Kien Giang
```{r}
quality_sense_only_KG <- quality_sense |> 
  dplyr::filter(location == "Kien Giang" ) 

glm_mucous_KG <- glmmTMB(Mucous ~ sample + (1|evaluator),
                              data = quality_sense_only_KG,
                              family = gaussian())

simulateResiduals(glm_mucous_KG, plot = TRUE)     #good
hist(simulateResiduals(glm_mucous_KG))            #good
testDispersion(simulateResiduals(glm_mucous_KG))            #good

cld((emmeans(glm_mucous_KG,  ~ sample)), Letters = letters)
#Differences between farms exist
```

#####Ca Mau
```{r}
quality_sense_only_CM <- quality_sense |> 
  dplyr::filter(location == "Ca Mau" ) 

glm_mucous_CM <- glmmTMB(Mucous ~ sample + (1|evaluator),
                              data = quality_sense_only_CM,
                              family = gaussian())

simulateResiduals(glm_mucous_CM, plot = TRUE)     #good
hist(simulateResiduals(glm_mucous_CM))            #good
testDispersion(simulateResiduals(glm_mucous_CM))            #good

cld((emmeans(glm_mucous_CM,  ~ sample)), Letters = letters)
#No difference between farms
```

#####Between regions
```{r}
quality_sense |> 
ggplot(aes(x = location, y = Mucous, fill = location)) + 
  geom_boxplot()

glm_mucous_locations <- glmmTMB(Mucous ~ location + (1|evaluator),
                              data = quality_sense,
                              family = gaussian())

simulateResiduals(glm_mucous_locations, plot = TRUE)     #good
hist(simulateResiduals(glm_mucous_locations))            #good
testDispersion(simulateResiduals(glm_mucous_locations))  #good

summary(glm_mucous_locations)
cld((emmeans(glm_mucous_locations,  ~ location, type = "response")), Letters = letters)
 # location          emmean     SE  df asymp.LCL asymp.UCL .group
 # Ba Ria - Vung Tau   8.40 0.0771 Inf      8.25      8.55  a    
 # Kien Giang          8.79 0.0736 Inf      8.64      8.93   b   
 # Ca Mau              9.18 0.0935 Inf      9.00      9.36    c  
```

####Odor
#####Ba Ria - Vung Tau
```{r}
quality_sense_only_BRVT <- quality_sense |> 
  dplyr::filter(location == "Ba Ria - Vung Tau" ) 

glm_modor_BRVT <- glmmTMB(Odor ~ sample + (1|evaluator),
                              data = quality_sense_only_BRVT,
                              family = gaussian())

simulateResiduals(glm_modor_BRVT, plot = TRUE)     #good
hist(simulateResiduals(glm_modor_BRVT))            #good
testDispersion(simulateResiduals(glm_modor_BRVT))            #good

cld((emmeans(glm_modor_BRVT,  ~ sample)), Letters = letters)
#Differences between farms exist
```

#####Kien Giang
```{r}
quality_sense_only_KG <- quality_sense |> 
  dplyr::filter(location == "Kien Giang" ) 

glm_odor_KG <- glmmTMB(Odor ~ sample + (1|evaluator),
                              data = quality_sense_only_KG,
                              family = gaussian())

simulateResiduals(glm_odor_KG, plot = TRUE)     #good
hist(simulateResiduals(glm_odor_KG))            #good, outlier
testDispersion(simulateResiduals(glm_odor_KG))            #good

cld((emmeans(glm_odor_KG,  ~ sample)), Letters = letters)
#Differences between farms exist
```

#####Ca Mau
```{r}
quality_sense_only_CM <- quality_sense |> 
  dplyr::filter(location == "Ca Mau" ) 


glm_odor_CM <- glmmTMB(Odor ~ sample + (1|evaluator),
                              data = quality_sense_only_CM,
                              family = gaussian())

simulateResiduals(glm_odor_CM, plot = TRUE)     #good
hist(simulateResiduals(glm_odor_CM))            #good
testZeroInflation(glm_odor_CM)                  #good

cld((emmeans(glm_odor_CM,  ~ sample)), Letters = letters)
#No difference between farms
```

#####Between regions
```{r}
quality_sense |> 
ggplot(aes(x = location, y = log(Odor), fill = location)) + 
  #geom_boxplot() + 
  geom_point(aes(colour = evaluator), 
             position = "jitter")

glm_odor_locations <- glmmTMB(log(Odor) ~ location + (1|evaluator),
                              data = quality_sense,
                              family = gaussian(), 
                              dispformula = ~location)

simulateResiduals(glm_odor_locations, plot = TRUE)     #uneven dispersion, need ~location and log
plotResiduals(glm_odor_locations, quality_sense$evaluator, xlab = "evaluator", main=NULL)#good
plotResiduals(glm_odor_locations, quality_sense$location, xlab = "location", main=NULL)#Kein Giang triggers, probably due to weird distribution. rest are OK so good to proceed
hist(simulateResiduals(glm_odor_locations))            #good
testDispersion(simulateResiduals(glm_odor_locations))  #good

summary(glm_odor_locations)
cld((emmeans(glm_odor_locations,  ~ location, type = "response")), Letters = letters)
 # location          emmean     SE  df asymp.LCL asymp.UCL .group
 # Ba Ria - Vung Tau   8.40 0.0771 Inf      8.25      8.55  a    
 # Kien Giang          8.79 0.0736 Inf      8.64      8.93   b   
 # Ca Mau              9.18 0.0935 Inf      9.00      9.36    c  
```

####Overall
#####Ba Ria - Vung Tau
```{r}
quality_sense_BRVT <- quality_sense |> 
  dplyr::filter(location == "Ba Ria - Vung Tau" ) 

glm_score_BRVT <- glmmTMB(Score ~ sample + (1|evaluator),
                              data = quality_sense_BRVT,
                              family = gaussian())

simulateResiduals(glm_score_BRVT, plot = TRUE)     #good
hist(simulateResiduals(glm_score_BRVT))            #good
testDispersion(simulateResiduals(glm_score_BRVT))            #good
testZeroInflation(glm_score_BRVT)                  #good

summary(glm_score_BRVT)
pairs(emmeans(glm_score_BRVT,  ~ sample)) 
cld((emmeans(glm_score_BRVT,  ~ sample)), Letters = letters)
#Differences between farms exist 
```

#####Kien Giang
```{r}
quality_sense_KG <- quality_sense |> 
  dplyr::filter(location == "Kien Giang" ) 

glm_score_KG <- glmmTMB(Score ~ sample + (1|evaluator),
                              data = quality_sense_KG,
                              family = gaussian())

simulateResiduals(glm_score_KG, plot = TRUE)     #good
hist(simulateResiduals(glm_score_KG))            #good
testZeroInflation(glm_score_KG)                  #good

summary(glm_score_KG)
pairs(emmeans(glm_score_KG,  ~ sample)) 
cld((emmeans(glm_score_KG,  ~ sample)), Letters = letters)
#Differences between farms exist 
```

#####Ca Mau
```{r}
quality_sense_CM <- quality_sense |> 
  dplyr::filter(location == "Ca Mau" ) 


glm_score_CM <- glmmTMB(Score ~ sample + (1|evaluator),
                              data = quality_sense_CM,
                              family = gaussian())

simulateResiduals(glm_score_CM, plot = TRUE)     #good
hist(simulateResiduals(glm_score_CM))            #good
testZeroInflation(glm_score_CM)                  #good

summary(glm_score_CM)
pairs(emmeans(glm_score_CM,  ~ sample)) 
cld((emmeans(glm_score_CM,  ~ sample)), Letters = letters)
#No difference between farms
```

#####Between regions
```{r}
quailty_sense_box <- quality_sense |> 
ggplot(aes(x = location, y = Score, fill = location)) + 
  geom_boxplot() +
  theme_minimal() + 
  scale_x_discrete(name = "") + 
  scale_y_continuous(limits = c(0, 10), 
                     breaks = seq(1, 10, 1)) + 
  scale_fill_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location", 
                         guide = "none") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black"), 
        axis.text = element_text(colour = "black"), 
        panel.grid = element_blank(), 
        axis.ticks = element_line(colour = "black")) + 
  geom_signif(comparisons = list(c("Ca Mau", "Kien Giang")), 
              annotations = c("NS")) + 
  annotate("text", x = 1, y = 9.5, label = "***") 



glm_score_locations <- glmmTMB(log(Score) ~ location + (1|evaluator),
                              data = quality_sense,
                              family = gaussian(), 
                              dispformula = ~location)

simulateResiduals(glm_score_locations, plot = TRUE)     #good - need log and ~ location to account for difference variance
hist(simulateResiduals(glm_score_locations))            #good
testDispersion(simulateResiduals(glm_score_locations))            #good
testZeroInflation(glm_score_locations)                  #good

summary(glm_score_locations)
cld((emmeans(glm_score_locations,  ~ location, type = "response")), Letters = letters)
 # location          response    SE  df lower.CL upper.CL .group
 # Ba Ria - Vung Tau     5.62 0.253 103     5.14     6.14  a    
 # Ca Mau                6.68 0.128 103     6.43     6.94   b   
 # Kien Giang            6.75 0.217 103     6.33     7.19   b 
```

#Chemical and Biological indicators
###Correlation matrix
```{r}
##bichem with each other
quality_comb_matrix <- 
  quality_comb |>  
  dplyr::group_by(sample) |> 
  dplyr::summarise(across(pH:score, mean, na.rm = TRUE)) |> 
  dplyr::select(pH:score)

res2 <- rcorr(as.matrix(quality_comb_matrix), type = c("spearman"))

res <- cor(quality_comb_matrix, use = "complete.obs", method = "spearman")
corrplot(res, type = "upper", order = "original", method = "number", 
         tl.col = "black")

testR <- cor.mtest(res, conf.level = 0.95)
corrplot(res, type = "upper", order = "original", method = "color", diag = FALSE, 
         tl.col = "black", tl.srt = 45,
         p.mat = testR$p, sig.level=c(0.001, 0.01, 0.05), pch.cex = 0.9,
         insig = "label_sig")
```

###pH
```{r}
glm_location_TVB_N <- glmmTMB(TVB_N ~ location + (1|sample), 
                           family = Gamma(link = "log"), 
                           data = quality_comb)

#checking fit
simulateResiduals(glm_location_TVB_N, plot = TRUE)     #qq good, Gamma makes fit better,
plotResiduals(glm_location_TVB_N, quality_comb$location, xlab = "location", main=NULL)

hist(simulateResiduals(glm_location_TVB_N))            #good
testDispersion(simulateResiduals(glm_location_TVB_N))

summary(glm_location_TVB_N) 
#yes influence of everything

cld((emmeans(glm_location_TVB_N,  ~ location, type = "response")), Letters = letters)
```

###TVB_N
```{r}
glm_location_TVB_N <- glmmTMB(TVB_N ~ location + (1|sample), 
                           family = Gamma(link = "log"), 
                           data = quality_comb)

#checking fit
simulateResiduals(glm_location_TVB_N, plot = TRUE)     #qq good, Gamma makes fit better,
plotResiduals(glm_location_TVB_N, quality_comb$location, xlab = "location", main=NULL)

hist(simulateResiduals(glm_location_TVB_N))            #good
testDispersion(simulateResiduals(glm_location_TVB_N))

summary(glm_location_TVB_N) 
#yes influence of everything

cld((emmeans(glm_location_TVB_N,  ~ location, type = "response")), Letters = letters)

```

###TBA
```{r}
glm_TVA <- glmmTMB((TBA) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())
simulateResiduals(glm_TVA, plot = TRUE)     #good
hist(simulateResiduals(glm_TVA))            #good
testDispersion(simulateResiduals(glm_TVA))

summary(glm_TVA) 
cld((emmeans(glm_TVA,  ~ location, type = "response")), Letters = letters)
#no difference
```

###FFA_% 
```{r}
glm_FFA <- glmmTMB((`FFA_%`) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian(), 
                              dispformula = ~location)

simulateResiduals(glm_FFA, plot = TRUE)     #levene triggered but visual OK (small sample size)
hist(simulateResiduals(glm_FFA))            #good
testDispersion(simulateResiduals(glm_FFA))
summary(glm_FFA) 
cld((emmeans(glm_FFA,  ~ location, type = "response")), Letters = letters)
#no difference 
```

###TMA_N
```{r}
glm_TMA_N <- glmmTMB((TMA_N) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_TMA_N, plot = TRUE)     #
hist(simulateResiduals(glm_TMA_N))            #good
testDispersion(simulateResiduals(glm_TMA_N))
summary(glm_TMA_N) 
cld((emmeans(glm_TMA_N,  ~ location, type = "response")), Letters = letters)
#no difference
```


###Cadaverine
```{r}
glm_Cadaverine <- glmmTMB(sqrt(Cadaverine) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Cadaverine, plot = TRUE)     #good
hist(simulateResiduals(glm_Cadaverine))            #good
testDispersion(simulateResiduals(glm_Cadaverine))
summary(glm_Cadaverine) 
cld((emmeans(glm_Cadaverine,  ~ location, type = "response")), Letters = letters)
#no difference 
```

###Histamine
```{r}
glm_Histamine <- glmmTMB((Histamine) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Histamine, plot = TRUE)     #good
hist(simulateResiduals(glm_Histamine))            #good
testDispersion(simulateResiduals(glm_Histamine))
summary(glm_Histamine) 
cld((emmeans(glm_Histamine,  ~ location, type = "response")), Letters = letters)
#no difference 
```

###Putrescine
```{r}
glm_Putrescine <- glmmTMB(sqrt(Putrescine) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Putrescine, plot = TRUE)     #
hist(simulateResiduals(glm_Putrescine))            #good
testDispersion(simulateResiduals(glm_Putrescine))
summary(glm_Putrescine) 
cld((emmeans(glm_Putrescine,  ~ location, type = "response")), Letters = letters)
#no difference 
```

###Vitamin_A
```{r}
glm_Vitamin_A <- glmmTMB(log(Vitamin_A) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Vitamin_A, plot = TRUE)     #good
hist(simulateResiduals(glm_Vitamin_A))            #good
testDispersion(simulateResiduals(glm_Vitamin_A))
summary(glm_Vitamin_A) 
cld((emmeans(glm_Vitamin_A,  ~ location, type = "response")), Letters = letters)
# location          response   SE  df asymp.LCL asymp.UCL .group
#  Ba Ria - Vung Tau     17.0 1.62 Inf      14.1      20.4  a    
#  Kien Giang            21.3 1.91 Inf      17.8      25.4  a    
#  Ca Mau                22.5 2.72 Inf      17.8      28.5  a 

Vitamin_A_box <- 
  quality_comb_mean |> 
ggplot(aes(location, Vitamin_A)) + 
  geom_boxplot(aes(fill = location)) +
  theme_minimal() + 
  scale_x_discrete(name = "", 
                   ) + 
  scale_y_continuous(limits = c(0, 45), 
                     breaks = seq(0, 45, 5), 
                     name = "Vitamin A (mg/kg)") + 
  scale_fill_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location", 
                         guide = "none") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black"), 
        axis.text = element_text(colour = "black"),
        axis.text.x=element_blank(),
        panel.grid = element_blank(), 
        axis.ticks = element_line(colour = "black")) +
  #geom_signif(comparisons = list(c("Ca Mau", "Kien Giang")), annotations = c("NS"))
  annotate("text", x = 2, y = 45, label = "NS") + 
    annotate("segment", x = 1, xend=3, y = 42)
```

###Vitamin_D3
```{r}
glm_Vitamin_D3 <- glmmTMB(log(Vitamin_D3) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian(), 
                          dispformula = ~location)

simulateResiduals(glm_Vitamin_D3, plot = TRUE)     #levene triggered but use dispformula to compensate
hist(simulateResiduals(glm_Vitamin_D3))            #good
testDispersion(simulateResiduals(glm_Vitamin_D3))
summary(glm_Vitamin_D3) 
cld((emmeans(glm_Vitamin_D3,  ~ location, type = "response")), Letters = letters)
 # location          response     SE  df asymp.LCL asymp.UCL .group
 # Ba Ria - Vung Tau    0.773 0.0469 Inf     0.686      0.87  a    
 # Ca Mau               1.153 0.0884 Inf     0.992      1.34   b   
 # Kien Giang           1.476 0.0844 Inf     1.320      1.65    c  

Vitamin_D3_box <- 
  quality_comb_mean |> 
ggplot(aes(location, Vitamin_D3)) + 
  geom_boxplot(aes(fill = location)) +
  theme_minimal() + 
  scale_x_discrete(name = "", 
                   ) + 
  scale_y_continuous(limits = c(0, 2.5), 
                     breaks = seq(0, 2.5, 0.5), 
                     name = "Vitamin D3 (mg/kg)") + 
  scale_fill_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location", 
                         guide = "none") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black"), 
        axis.text = element_text(colour = "black"),
        axis.text.x=element_blank(),
        panel.grid = element_blank(), 
        axis.ticks = element_line(colour = "black")) +
  # geom_signif(comparisons = list(c("Ca Mau", "Kien Giang")),
  #             annotations = c("***")) +
  annotate("text", x = 2, y = 2.45, label = "***") + 
    annotate("segment", x = 1, xend = 3, y = 2.4, colour = "black")
```

###Vitamin_E
```{r}
glm_Vitamin_E <- glmmTMB(log(Vitamin_E) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Vitamin_E, plot = TRUE)     #outlier detected
hist(simulateResiduals(glm_Vitamin_E))            #good
testDispersion(simulateResiduals(glm_Vitamin_E))
summary(glm_Vitamin_E) 
cld((emmeans(glm_Vitamin_E,  ~ location, type = "response")), Letters = letters)
 # location          response   SE  df asymp.LCL asymp.UCL .group
 # Kien Giang            11.7 1.77 Inf      8.74      15.8  a    
 # Ba Ria - Vung Tau     12.6 2.01 Inf      9.22      17.2  a    
 # Ca Mau                23.5 4.73 Inf     15.79      34.8   b

Vitamin_E_box <- 
  quality_comb_mean |> 
ggplot(aes(location, Vitamin_E)) + 
  geom_boxplot(aes(fill = location)) +
  theme_minimal() + 
  scale_x_discrete(name = "Location", 
                   ) + 
  scale_y_continuous(limits = c(0, 52), 
                     breaks = seq(0, 50, 10), 
                     name = "Vitamin E (mg/kg)") + 
  scale_fill_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black"), 
        axis.text = element_text(colour = "black"),
        panel.grid = element_blank(), 
        axis.ticks = element_line(colour = "black"), 
        legend.position = "none") +
    annotate("text", x = 1.45, y = 51, label = "**") + 
    annotate("segment", x = 1, xend = 1.9 , y = 50, colour = "black") + 
    annotate("text", x = 2.55, y = 51, label = "**") + 
    annotate("segment", x = 2.1, xend = 3, y = 50, colour = "black")

```


###TVC_CFU
```{r}
glm_TVC_CFU <- glmmTMB(log10(TVC_CFU) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian(), 
                       dispformula = ~location)

simulateResiduals(glm_TVC_CFU, plot = TRUE)     #
plotResiduals(glm_TVC_CFU, quality_comb$location, xlab = "location", main=NULL)
hist(simulateResiduals(glm_TVC_CFU))            #good
testDispersion(simulateResiduals(glm_TVC_CFU))

cld((emmeans(glm_TVC_CFU,  ~ location, type = "response")), Letters = letters)
 # location          response       SE  df asymp.LCL asymp.UCL .group
 # Kien Giang        6.00e+07 3.77e+07 Inf  18907966  2.26e+08  a    
 # Ba Ria - Vung Tau 9.57e+07 6.73e+07 Inf  26579409  4.24e+08  a    
 # Ca Mau            3.70e+08 3.80e+08 Inf  59838299  3.46e+09  a    
 
quality_comb_mean |>  
  ggplot(aes(score, log10(TVC_CFU))) + 
  geom_point(aes(colour = location), size = 3) + 
  geom_smooth(method = "lm", 
              colour = "grey", 
              alpha = 0.3) +
  theme_minimal() + 
  scale_x_continuous(limits = c(1, 10), 
                     breaks = seq(1, 10, 1),
                     name = "Sensory score") + 
  scale_y_continuous(limits = c(6, 11), 
                     breaks = seq(6, 11, 1), 
                     name = "TVC (log10(CFU))") + 
  scale_colour_paletteer_d(palette = "fishualize::Epinephelus_lanceolatus", 
                           direction = 1, 
                           name = "Location") +
  theme(axis.line = element_line(colour = "black"), 
        legend.text = element_text(colour = "black", size = 12),
        legend.position = "bottom",
        axis.text = element_text(colour = "black", size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank())
```

###Enterobacteriaceae_CFU
```{r}
glm_EB <- glmmTMB(log10(Enterobacteriaceae_CFU) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian(), 
                  dispformula = ~location)

simulateResiduals(glm_EB, plot = TRUE)     #
hist(simulateResiduals(glm_EB))            #good
testDispersion(simulateResiduals(glm_EB))
cld((emmeans(glm_EB,  ~ location, type = "response")), Letters = letters)
 # location          response    SE  df asymp.LCL asymp.UCL .group
 # Kien Giang             930   665 Inf       229      3775  a    
 # Ba Ria - Vung Tau    21344 16200 Inf      4829     94342   b   
 # Ca Mau               26516 25400 Inf      4048    173694   b  
```

###Pseudomonas_CFU
```{r}
glm_Psuedo <- glmmTMB(log10(Pseudomonas_CFU) ~ location + (1|sample), 
                              data = quality_comb,
                              family = gaussian())

simulateResiduals(glm_Psuedo, plot = TRUE)     #
hist(simulateResiduals(glm_Psuedo))            #good
testDispersion(simulateResiduals(glm_Psuedo))
cld((emmeans(glm_Psuedo,  ~ location, type = "response")), Letters = letters)
# location          response    SE df lower.CL upper.CL .group
 # Kien Giang            1145   499 61      479     2736  a    
 # Ca Mau               26456 15467 61     8219    85158   b   
 # Ba Ria - Vung Tau    55876 25825 61    22174   140801   b
```

###Threshholds exceeded
```{r}
quality_comb |> 
  group_by(sample) |>
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE))) |>  
  mutate(TVBN_ex = case_when(TVB_N>35~1, TVB_N<35~0), 
         Hist_ex = case_when(Histamine>404~1,Histamine<404~0), 
         TVC_ex = case_when(TVC_CFU>(10^7)~1,TVC_CFU<(10^7)~0)) |> 
  ungroup() |> 
  summarise(across(where(is.numeric), ~ sum(.x, na.rm = TRUE))) |> 
  mutate(TVBN_ex_per = round(TVBN_ex/22*100,0), 
         Hist_ex_per = round(Hist_ex/22*100,0), 
         TVC_ex_per = round(TVC_ex/22*100, 0)) |> 
  dplyr::select(TVBN_ex, TVBN_ex_per, Hist_ex, Hist_ex_per, TVC_ex, TVC_ex_per)
```

##Combine plots
```{r}
ggarrange(TVB_N_plot, TVB_score, nrow = 2, ncol = 1, labels = c("a", "b"))

ggarrange(Vitamin_A_box, Vitamin_D3_box, Vitamin_E_box, nrow = 3, ncol = 1, labels = c("a", "b", "c"))
```


